manuscript - APP

### 2018-08-08 R/manuscript_app_alt_clean.Rmd
fix ratio function error

```{r echo=FALSE}
# Exp 1b
df_exp1b <- 
  readRDS(
    file.path(data_pth, "exp1b", "responses", "responses_150622.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_straight = (targetk > restk),
         ratio = (besselI(targetk,0) * exp(targetk)) / (besselI(restk,0) * exp(restk)),
         ratio_abs = abs(log((besselI(targetk,0) * exp(targetk))) / (besselI(restk,0) * exp(restk))))
participants_exp1b <- 
  read.csv(file.path(data_pth, "exp1b", "participants_150526.csv"), fileEncoding = "UTF8")

@@

  theme(aspect.ratio = 1) + 
  xlab("kl distance") + ylab("Accuracy") +scale_x_continuous(trans ="log")
```

>>>>

```{r echo=FALSE}
# Exp 1b
df_exp1b <- 
  readRDS(
    file.path(data_pth, "exp1b", "responses", "responses_150622.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_straight = (targetk > restk),
         ratio = (besselI(restk,0) * exp(targetk)) / (besselI(targetk,0) * exp(restk)),
         ratio_abs = abs(log((besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))),
         ratio_abs = abs(log(
           (besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))))
participants_exp1b <- 
  read.csv(file.path(data_pth, "exp1b", "participants_150526.csv"), fileEncoding = "UTF8")

@@

  theme(aspect.ratio = 1) + 
  xlab("ratio") + ylab("Accuracy") +scale_x_continuous(trans ="log")
```
